Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2015-04-07 Paper.tex
createdata -> codedeposit

The application of rewards to a block involves raising the balance of the accounts of the coinbase address of the block and each ommer by a certain amount. We raise the block's coinbase account by $R_b$; for each ommer, we raise the block's coinbase by an additional $\frac{1}{32}$ of the block reward and the coinbase of the ommer by $\frac{15}{16}$ of the reward. Formally we define the function $\Omega$:
\begin{eqnarray}
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\boldsymbol{\sigma}'[{B_H}_c]_b & = & \boldsymbol{\sigma}[{B_H}_c]_b + (1 + \frac{|B_\mathbf{U}|}{32})R_b \\
\forall_{U \in B_\mathbf{U}} \; \boldsymbol{\sigma}'[U_c]_b & = & \boldsymbol{\sigma}[U_c]_b + \frac{15}{16}R_b
\end{eqnarray}

>>>>

The application of rewards to a block involves raising the balance of the accounts of the coinbase address of the block and each ommer by a certain amount. We raise the block's coinbase account by $R_b$; for each ommer, we raise the block's coinbase by an additional $\frac{1}{32}$ of the block reward and the coinbase of the ommer gets rewarded depending on the block number. Formally we define the function $\Omega$:
\begin{eqnarray}
\Omega(B, \boldsymbol{\sigma}) & \equiv & \boldsymbol{\sigma}': \boldsymbol{\sigma}' = \boldsymbol{\sigma} \quad \text{except:} \\
\boldsymbol{\sigma}'[{B_H}_c]_b & = & \boldsymbol{\sigma}[{B_H}_c]_b + (1 + \frac{|B_\mathbf{U}|}{32})R_b \\
\forall_{U \in B_\mathbf{U}}: \\ \nonumber
 \boldsymbol{\sigma}'[U_c]_b & = & \boldsymbol{\sigma}[U_c]_b + (1 - \frac{1}{8} (U_i - {B_H}_i)) R_b 
\end{eqnarray}
